\section{Deformation Quantization and Algebraic Index}\label{sec:dqai}

Recall that we discussed in the \nameref{subsec:hker}, the family $\lcb I[L]\rcb_{L>0}$ satisfies the HRG.
\bea
\tikzset{every picture/.style={line width=0.75pt}} 
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]

%Straight Lines [id:da977711475048066] 
\draw    (10.5,100.67) -- (237.5,100.67) ;
\draw [shift={(240.5,100.67)}, rotate = 180] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;

% Text Node
\draw (4,78.23) node [anchor=north west][inner sep=0.75pt]    {$0$};
% Text Node
\draw (3.12,96) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize,rotate=-0.88]  {$\blt$};
% Text Node
\draw (58,96) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize,rotate=-0.88]  {$\blt$};
% Text Node
\draw (166.12,96) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize,rotate=-0.88]  {$\blt$};
% Text Node
\draw (58,77.23) node [anchor=north west][inner sep=0.75pt]    {$L_{1}$};
% Text Node
\draw (165.5,76.23) node [anchor=north west][inner sep=0.75pt]    {$L_{2}$};
% Text Node
\draw (245.5,93.07) node [anchor=north west][inner sep=0.75pt]    {$L$};
% Text Node
\draw (40.5,108.07) node [anchor=north west][inner sep=0.75pt]    {$I[L_{1}]$};
% Text Node
\draw (152.5,108.07) node [anchor=north west][inner sep=0.75pt]    {$I[L_{2}]$};
% Text Node
\draw (100,106.57) node [anchor=north west][inner sep=0.75pt]    {$\overset{\text{HRG}}{\leadsto}$};
\end{tikzpicture}
\eea
At $L\to 0$, we use the counter-term method to reduce the ill-defined theory with UV divergence to a well-defined effective theory.
At each $L>0$, we have a well-defined effective BV operator $\Delta_L$, which is a contraction with the smooth kernel $K_L$ representing $e^{-L\lsb Q,Q^\dagger\rsb}$. This leads to the effective DGBV, $\lb \sO(\cE), Q, \Delta_L\rb$, in which the corresponding $I[L]$ solves the QME.

Let $\bH=\lcb \left. \varphi\in\cE\ \right|\ \lsb Q,Q^\dagger\rsb\varphi=0\rcb\ = 
\lcb \left. \varphi\in\cE\ \right|\  Q\varphi=Q^\dagger\varphi=0\rcb\ \simeq H^\blt\lb \cE,Q\rb$. $\bH$ is called the space of \textbf{harmonics} (or the \textbf{zero modes}), which is a finite-dimensional space (by Hodge theory).
Then we have
\bea
\begin{tikzcd}
\infty-\text{dimensional } (-1)-\text{symplectic geometry } (\cE,Q,\omega)  \ar[d, "L\to\infty"] \\
\text{finite-dimensional } (-1)-\text{symplectic geometry } (\bH,\omega_H
=\left. \omega \right|_{\bH})
\end{tikzcd}
\eea

The BV operator $\Delta_H$ associated with $\omega_H^{-1}$ is $\Delta_H=\Delta_\infty$. On the complete story of BV quantization, as depicted in the following diagram,
\bea
\tikzset{every picture/.style={line width=0.75pt}} 
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]

%Straight Lines [id:da977711475048066] 
\draw    (10.5,100.67) -- (237.5,100.67) ;
\draw [shift={(240.5,100.67)}, rotate = 180] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;

% Text Node
\draw (4,78.23) node [anchor=north west][inner sep=0.75pt]    {$0$};
% Text Node
\draw (3.12,96) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize,rotate=-0.88]  {$\blt$};

% Text Node
\draw (245.5,93.07) node [anchor=north west][inner sep=0.75pt]    {$L=\infty$};
\end{tikzpicture}
\eea
$I[\infty]$ solves the QME for $\lb \sO(\bH),\Delta_H\rb$ at $L=\infty$. This is an interesting point where we will find some finite-dimensional geometric data, leading to the index theory.

Our next goal is to use the method we have discussed so far to do \emph{geometry and topology}.
We will explain two main examples:
\bi[(1)]
\item 1d example: topological quantum mechanics and algebraic index.
\textsc{References}: \cite{Grady:2015ica,Gui:2019ldd}.

\item 2d example: chiral CFT and chiral index. 
\textsc{References}: \cite{Li:2016gcb,Gui:2021dci}.
\ei

\subsection{Deformation quantization}
\begin{defn}
A \textbf{Poisson manifold} is a pair $\lb X,P\rb$, where $X$ is a smooth manifold, and $P\in \Gamma(X, \asym^2 TX)$ satisfying $\lcb P,P\rcb_{\text{SN}}=0$.
\end{defn}
$\lcb -,-\rcb_{\text{SN}}$ is the \emph{Schouten-Nijenhuis bracket}. $P$ is called the \textbf{Poisson tensor/bi-vector}. In local coordinates, we can write 
\bea P=\sum_{i,j} P^{ij}(x)\p_i \wedge \p_j.\eea
It defines a \emph{Poisson bracket} $\lcb-,-\rcb_P$ on $C^\infty(x)$:
\bea \lcb f,g\rcb_P \coloneqq \sum_{i,j} P^{ij}\p_i f \p_j g,\quad \forall f,g\in C^\infty(x).\eea
Here $\lcb P,P\rcb_{\text{SN}}=0$ implies that $\lcb-,-\rcb_P$ satisfies Jacobi identity. Hence $\lcb-,-\rcb_P$ naturally defines the Poisson algebra $\lb C^\infty(x), \lcb-,-\rcb_P\rb$.

\begin{eg}
Let $(X,\omega)$ be a symplectic manifold, where $\omega= \hf\sum_{i,j} \omega_{ij} dx^i \wedge dx^j$ is a symplectic 2-form. Let 
$P=\omega^{-1}=\hf \sum_{i,j} \omega^{ij} \p_i \wedge \p_j$,
where $(\omega^{ij})$ is the inverse of $(\omega_{ij})$. Then $d\omega=0 \LRA \lcb P,P\rcb_{\text{SN}}=0$. Hence $(X,\omega^{-1})$ is a Poisson manifold.
\end{eg}

\paragraph{Deformation quantization.}
This method was developed in the series of papers by Bayen, Flato, Fronsdal, Lichnerowicz, Sternheimer (BFFLS) \cite{bayen1977quantum,BAYEN197861,BAYEN1978111}. The space of the real-valued (or complex-valued) functions on a phase space admits
two algebraic structures: a structure of \emph{associative algebra} given by the usual product of
functions and a structure of Lie algebra given by the \emph{Poisson bracket}. The study of the
properties of the deformations (in a suitable sense) of these two structures gives a new
invariant approach for Quantum Mechanics (QM) and Quantum Field Theory (QFT).
\bea
\begin{tikzcd}
\text{Poisson Lie algebra}
\arrow[r, bend left, "\text{quantization}"] & \arrow[l, bend left, "\hbar\to 0"] \text{Associative algebra} 
\end{tikzcd}\eea
This is essentially the quantization method in quantum mechanics, in which a function $f$ on the classical phase space is quantized to an operator $\widehat{f}$.

\begin{defn}
A \textbf{star-product} on a Poisson manifold $(X,P)$ is a $\bR[[ \hbar]]$-bilinear map
\bea C^\infty(x)[[ \hbar]] \times C^\infty(x)[[ \hbar]] \to C^\infty(x)[[ \hbar]], \qquad 
f \times g \mapsto f\star g=\sum_{k\geq 0} \hbar^k c_k\lb f,g\rb 
\eea
such that
\bi[(1)]
\item $\star$ is associative: $\lb f\star g\rb \star h=f\star \lb g\star h\rb$,
\item $f\star g= fg+\cO(\hbar), \quad \forall f,g\in C^\infty(x)$,
\item $\star$ is non-commutative: $\hf \lb f\star g-g\star f\rb=\hbar\lcb f,g\rcb+\cO(\hbar^2), \quad \forall f,g\in C^\infty(x)$,
\item $c_k: C^\infty(x)\times C^\infty(x)\to C^\infty(x)$ is a bidifferential operator. 
\ei
Then $\lb C^\infty(x)[[\hbar]], \star\rb$ is called a \textbf{deformation quantization} of $\lb X,P\rb$.
\end{defn}

The deformation quantization is purely algebraic; no Hilbert space is involved.
The \emph{existence} of deformation quantization is highly nontrivial. In particular, the existence of formal star product on symplectic manifolds was proved by de Wilde-LeConte \cite{de1983existence} and Fedosov \cite{fedosov1994simple}.
More generally, Kontsevich \cite{Kontsevich:1997vb} gave the complete solution for general Poisson manifold. 

\begin{eg}[Moyal-Weyl product]
Let $X$ be a phase space, $\bR^{2n}$, with a symplectic form $\omega=\hf \sum_{i,j} \omega_{ij} dx^i \wedge dx^j$ where $\omega_{ij}$ is a constant. The Poisson tensor is $P=\hf \sum_{i,j} \omega^{ij} \p_i\wedge \p_j$. Given $f(x),g(x)\in C^\infty\lb \bR^{2n}\rb$, define the Moyal-Weyl product $\star$ by
\bea
(f\star g)(x)=\left. \exp{\lb \frac{\hbar}{2} \sum_{i,j} \omega^{ij} \frac{\p}{\p y^i}\frac{\p}{\p z^j}\rb}\right|_{y=z=x} f(y) g(z)
\eea
or pictorially,\\
\bea 
    \begin{fmffile}{fmw}
    \begin{tabular}{c}
        \begin{fmfgraph*}(150,50)
                \fmfleft{i1,i2}
                \fmfright{o1,o2}
    
                \fmf{plain,tension=4}{i1,v1}
                \fmf{plain,tension=4}{i2,v1}
                \fmf{plain,tension=4}{v2,o1}
                \fmf{plain,tension=4}{v2,o2}
        
                \fmf{plain,left=1,tension=0.4,label=$\frac{\p}{\p x^i} \omega^{ij} \frac{\p}{\p x^j}$,label.side=left}{v1,v2}
                \fmf{plain,left=0.5,tension=0.8}{v1,v2}
                \fmf{phantom,right=0.2,tension=2,label=$\cdot$,label.side=left}{v1,v2}
                \fmf{phantom,right=0.5,tension=0.8,label=$\cdot$,label.side=left}{v1,v2}
                \fmf{phantom,right=0.8,tension=0.6,label=$\cdot$,label.side=left}{v1,v2}
                \fmf{plain,right=1,tension=0.4}{v1,v2}
                
                \fmfv{label=$f\ $,label.angle=180,decor.shape=circle,decor.filled=full,decor.size=2thick}{v1}
                \fmfv{label=$\ g$,label.angle=0,decor.shape=circle,decor.filled=full,decor.size=2thick}{v2}
        \end{fmfgraph*}
        \end{tabular}
    \end{fmffile}
\eea
Then $\star$ defines a deformation quantization.
\end{eg}

\begin{rmk}
If $\omega^{ij}\neq$ constant, then the above formula does not work. 
\end{rmk}

For convenience, we can describe a formal version. Let $\lb V,\omega\rb$ be a linear symplectic space, where $V\simeq \bR^{2n}$ and $\omega: \asym^2 V\to \bR$ is a symplectic pairing. Write 
\bea\widehat{\sO}(V)\coloneqq \widehat{\sym}(V^\vee)=\prod_{k\geq 0} \sym^k(V^\vee),\eea
where $V^\vee=\on{Hom}(V,\bR)$ is the linear dual of $V$. Then the Moyal-Weyl product defines an associative algebra $\lb \widehat{\sO}(V)[[ \hbar]],\star\rb$, called the \textbf{(formal) Weyl algebra}. On the other hand, let 
\bea\widehat{\Omega}^{-\blt}_{V}\coloneqq \widehat{\sO}(V) \otimes \asym^{-\blt}(V^\vee).
\eea
Here $\widehat{\Omega}^{-p}_{V}\coloneqq \widehat{\sO}(V) \otimes \asym^{p}(V^\vee)$ are the (formal) $p$-forms sitting in degree $-p$. Let $d_V: \widehat{\Omega}^{-p}_{V} \to \widehat{\Omega}^{-(p+1)}_{V}$ be de Rham differential. Let $\Pi=\omega^{-1}\in\asym^2 V$ be the Poisson tensor and $\iota_\Pi: \widehat{\Omega}^{-\blt}_{V}\to \widehat{\Omega}^{-(\blt-2)}_{V}$ be the contraction with $\Pi$. Let 
\bea\Delta=\cL_\Pi=\lsb d_V,\iota_\Pi\rsb: \widehat{\Omega}^{-\blt}_{V}\to\widehat{\Omega}^{-(\blt-1)}_{V}\eea
be the Lie derivative. Thus $\lb \widehat{\Omega}^{-\blt}_{V},\Delta\rb$ defines a BV algebra. Geometrically, this leads to Koszul-Brylinski complex/homology. Physically, this is the effective geometry on \emph{zero modes} of topological quantum mechanics as we will see.

\subsection{Fedosov quantization}
We will focus on \emph{symplectic manifolds} now. Fedosov \cite{fedosov1994simple} gave a simple and geometric construction of deformation quantization on symplectic cases. 
On a symplectic manifold $(X,\omega)$, the tangent plane $T_p X$ at each point $p \in X$ 
is a linear symplectic space. Quantum fluctuations deform the algebra of functions on $T_p X$ to the
associated \emph{Weyl algebra}. These pointwise Weyl algebras form a vector bundle --- the \emph{Weyl bundle} $\cW(X)$ on $X$.
\begin{defn}
Let $(X,\omega)$ be a symplectic manifold.
We define the \textbf{Weyl bundle} 
\bea \cW(X)\coloneqq \prod_{k\geq 0}\sym^k\lb T^\ast X\rb[[ \hbar]].\eea
So at each point $p\in X$, its fiber is
\bea \left. \cW(X)\right|_p= \widehat{\sO}\lb T_p X\rb[[\hbar]].\eea
\end{defn}
A local section of $\cW(X)$ is 
\bea \sigma(x,y)=\sum_{k,l\geq 0}\hbar^k a_{k,i_1\cdots i_l}(x) y^{i_1}\cdots y^{i_l},\eea
where $\lcb x\rcb$ are the base coordinates and $\lcb y\rcb$ are the fiber coordinates; $a_{k,i_1\cdots i_l}(x)$ are smooth functions.
Since $\lb T_p X, \left.\omega\right|_{T_p X}\rb$ is linear symplectic, we have a fiberwise Moyal-Weyl product, still denoted by $\star$. Thus $\lb \cW(X),\star\rb$ defines the $\infty$-dimensional bundle of algebras.

Let $\nabla$ be a connection on $TX$ which is torsion-free and compatible with $\omega$ (i.e. $\nabla \omega=0$). Such connection is called a \textbf{symplectic connection} (which always exist and is not unique). $\nabla$ induces a connection on all tensors. In particular, it defines a connection on $\cW(X)$, still denoted by $\nabla$. Its curvature is
\bea \nabla^2 \sigma=\frac{1}{\hbar}\lsb R_\nabla, \sigma\rsb_\star, \quad \forall \sigma\in \Gamma(X,\cW(X))\eea
where $R_\nabla=\frac{1}{4}R_{ijkl} y^i y^j dx^k \wedge dx^l \in \Omega^2(X,\cW(X))$ is a 2-form valued in the Weyl bundle $\cW(X)$; $R_{ijkl}=\omega_{im}R^m{}_{jkl}$ is a curvature form contracted with the symplectic pairing.

\paragraph{Fedosov connection.}
Given a sequence of closed 2-forms $\lcb \omega_k\rcb_{k\geq 1}$ on $X$, there exists a unique (up to gauge) connection on $\cW(X)$ of the form $\nabla+\frac{1}{\hbar}\lsb \gamma,-\rsb_\star$, where $\gamma\in\Omega^1\lb X, \cW(X)\rb$ is a $\cW(X)$-valued 1-form, satisfying some initial conditions and the equation 
\bea \nabla\gamma+\frac{1}{2\hbar}\lsb \gamma,\gamma\rsb_\star+R_\nabla=\omega_\hbar\qquad \text{(Fedosov equation)}\eea
where $\omega_{\hbar}= -\omega+ \sum_{k\geq 1}\hbar^k \omega_k$. 
Let 
\bea D= \nabla+\frac{1}{\hbar}\lsb \gamma,-\rsb_\star\eea
be the \textbf{Fedosov connection}. Then the Fedosov equation implies $D^2=\frac{1}{\hbar}\lsb\omega_\hbar,-\rsb_\star=0$, where $\omega_\hbar$ is constant along each fiber, and thus a central term.
So we obtain a flat connection $D$ on $\cW(X)$. 
Fedosov connection is the geometric
interpretation of the QME \cite{Grady:2015ica}.

Let $\cW_D(X)\coloneqq \lcb \left.\sigma\in\Gamma(X,\cW(X))\ \right|\ D\sigma=0 \rcb$ be the space of flat sections. Then $\lb \cW_D(X),\star\rb$ is an associative algebra.
Let 
\bea\sigma: \cW_D(X)\to C^\infty(X)[[\hbar]]\eea
be a \textbf{symbol map} by sending $y\mapsto 0$. Then $\sigma$ is an isomorphism, and 
\bea f\star g \mapsto \sigma\lb \sigma^{-1}\lb f\rb\star \sigma^{-1}\lb g\rb\rb\eea
defines a \textbf{deformation quantization}. $\omega_\hbar$ is the corresponding \textbf{characteristic class} (or \textbf{moduli}).

\subsection{Algebraic index theorem}
Given a deformation quantization $\lb C^\infty(X)[[\hbar]],\star \rb$ on a symplectic manifold with characteristic class $\omega_\hbar$, there exists a unique \textbf{trace map}
\bea \Tr: C^\infty(X)[[\hbar]] \to \bR ((\hbar))\eea
satisfying a normalization condition and the trace property:
\bea \Tr \lb f\star g\rb=\Tr \lb g\star f\rb.\eea
Then the index is obtained as the partition function of the theory, which can be formulated as 
\bea \on{Index}=\Tr(1)=\int_X e^{\omega_\hbar/\hbar} \widehat{A}(X),\eea
where $\widehat{A}(X)$ is the \emph{(formal) $\widehat{A}$-genus} of $X$.
This is the simplest version of \textbf{algebraic index theorem} formulated by Fedosov and Nest-Tsygan as the algebraic analogue of \emph{Atiyah-Singer index theorem}. 

We can similarly construct a \emph{deformation quantization} for $C^\infty\lb X,\on{End}(E)\rb[[\hbar]]$ and construct the trace map, then we have $\Tr(1)=\int_X e^{\omega_\hbar/\hbar}\on{Ch}(E) \widehat{A}(X)$, where $\on{Ch}(E)$ is the Chern character of the vector bundle $E$ over $X$.

\subsection{Relation with QFT}
In supersymmetric (SUSY) QFT, \emph{localization} often appears, in which the path integral on $\cE$ is often localized effectively to an equivalent integral on a finite-dimensional space $M\subset \cE$ describing some interesting moduli space:
\bea \int_\cE e^{iS/\hbar}= \int_M \lb -\rb.\eea

In topological QM, we find
\bea \int_{\on{Map}(S^1,X)} e^{-S/\hbar}\overset{\hbar\to 0}{=} \int_X \lb -\rb,\eea
where $\on{Map}(S^1,X)$ is a loop space, and $\int_X$ indicates the localization to a \emph{constant map}.
The path integral will be captured exactly by an effective theory in the formal neighborhood of
constant maps inside the full mapping space. Exact semi-classical approximation in $\hbar\to 0$ allows
us to reduce the path integral into a meaningful integral on the moduli space of constant maps, i.e., $X$.
The left-hand side usually gives a physics presentation of the analytic index of certain elliptic operator; the
right-hand side will end up with integrals of various curvature forms representing the topological index.

\begin{figure}[!htpb]\centering 
\tikzset{every picture/.style={line width=0.75pt}}         
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%Shape: Ellipse [id:dp23192014552632334] 
\draw   (34.83,63.04) .. controls (34.83,50.68) and (44.85,40.67) .. (57.21,40.67) .. controls (69.57,40.67) and (79.59,50.68) .. (79.59,63.04) .. controls (79.59,75.4) and (69.57,85.42) .. (57.21,85.42) .. controls (44.85,85.42) and (34.83,75.4) .. (34.83,63.04) -- cycle ;
%Straight Lines [id:da1794274167676957] 
\draw    (86.58,66.97) -- (118.38,66.97) ;
\draw [shift={(120.38,66.97)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Shape: Polygon Curved [id:ds4925647269289568] 
\draw   (138.44,47.45) .. controls (149.5,38.5) and (157,37) .. (179.23,45.99) .. controls (201.46,54.98) and (210.5,71.5) .. (190.3,83.87) .. controls (170.1,96.23) and (149.5,78) .. (135.24,78.33) .. controls (120.97,78.66) and (127.38,56.39) .. (138.44,47.45) -- cycle ;
%Shape: Ellipse [id:dp9869721752408005] 
\draw  [fill={rgb, 255:red, 144; green, 19; blue, 254 }  ,fill opacity=1 ] (138.15,62.89) .. controls (138.15,57.58) and (142.45,53.27) .. (147.76,53.27) .. controls (153.07,53.27) and (157.38,57.58) .. (157.38,62.89) .. controls (157.38,68.2) and (153.07,72.5) .. (147.76,72.5) .. controls (142.45,72.5) and (138.15,68.2) .. (138.15,62.89) -- cycle ;
%Curve Lines [id:da32709083755427515] 
\draw    (131,100.5) .. controls (127.97,94.38) and (114.35,86.96) .. (138.6,71.18) ;
\draw [shift={(140.96,69.69)}, rotate = 148.53] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
%Shape: Ellipse [id:dp7711772783086626] 
\draw   (280.67,60.39) .. controls (280.67,50.6) and (288.6,42.67) .. (298.39,42.67) .. controls (308.18,42.67) and (316.11,50.6) .. (316.11,60.39) .. controls (316.11,70.18) and (308.18,78.11) .. (298.39,78.11) .. controls (288.6,78.11) and (280.67,70.18) .. (280.67,60.39) -- cycle ;
%Straight Lines [id:da8438423211152051] 
\draw    (322.07,59.76) -- (355.03,59.76) ;
\draw [shift={(357.03,59.76)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Shape: Ellipse [id:dp2958661722082001] 
\draw  [fill={rgb, 255:red, 144; green, 19; blue, 254 }  ,fill opacity=1 ] (363.86,59.81) .. controls (363.86,49.48) and (372.24,41.1) .. (382.57,41.1) .. controls (392.91,41.1) and (401.28,49.48) .. (401.28,59.81) .. controls (401.28,70.15) and (392.91,78.52) .. (382.57,78.52) .. controls (372.24,78.52) and (363.86,70.15) .. (363.86,59.81) -- cycle ;

% Text Node
\draw (35.94,87.75) node [anchor=north west][inner sep=0.75pt]    {$S^{1}$};
% Text Node
\draw (79.29,98.35) node [anchor=north west][inner sep=0.75pt]   [align=left] {localized effective theory};
% Text Node
\draw (190.64,36.72) node [anchor=north west][inner sep=0.75pt]    {$X$};
% Text Node
\draw (276.88,80.5) node [anchor=north west][inner sep=0.75pt]    {$S^{1}$};
% Text Node
\draw (402.6,50.7) node [anchor=north west][inner sep=0.75pt]    {$\simeq \mathbb{R}^{2n}$};
\end{tikzpicture}
\end{figure}

Geometrically, a loop space is mapped to a localized neighborhood of a point in $X$ (specified by the constant map), where a localized effective theory exists.
Locally, by the choice of Darboux coordinates, $X$ can be thought of as a standard phase space, $\bR^{2n}$. 
The loop spaces are then glued together on $X$ as a family of effective field theory. This can be done rigorously within the framework of effective BV quantization:
\begin{itemize}
    \item effective action $\leadsto \gamma$,
    \item QME $\leadsto$ Fedosov equation,
    \item BV integral $\leadsto$ trace map,
    \item partition function $\leadsto$ algebraic index.
\end{itemize}
In the next section, we will present a physics ``derivation'' of the index theorem.
